---
title: "Economic Analysis Results"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    latex_engine: xelatex
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{float}
  - \usepackage{unicode-math}
  - \usepackage{geometry}
  - \usepackage{caption}
  - \usepackage{lscape}
  - \usepackage{tabularray}
  - \usepackage{graphicx}
  - \usepackage{codehigh}
  - \usepackage[normalem]{ulem}
  - \geometry{margin=1in}
  - \captionsetup{width=0.9\textwidth, font=small}
  - \renewcommand{\arraystretch}{1.2}
  - \UseTblrLibrary{booktabs}
  - \UseTblrLibrary{siunitx}
  - \usepackage{threeparttable}
---

# Summary Statistics
```{r, echo=FALSE}
options(knitr.kable.NA = "")
knitr::kable(state_summary,
  format = "latex",
  booktabs = TRUE,
  longtable = TRUE,
  digits = 2,
  caption = "State Summary Statistics",
  col.names = c("State", "Avg Employment", "Avg Wage", "N Industries", "Wage Inequality"),
  align = c("l", rep("r", 4)))
```

\newpage
# Regression Models

## COVID Impact Models
1. Employment COVID Impact:
   \[ \log(Employment_{ist}) = \beta_0 + \beta_1 COVID_t + \alpha_s + \gamma_i + \epsilon_{ist} \]
   - Shows how employment levels changed during COVID (2020 onwards)

2. Wage COVID Impact:
   \[ \log(Wage_{ist}) = \beta_0 + \beta_1 COVID_t + \alpha_s + \gamma_i + \epsilon_{ist} \]
   - Shows how wages changed during COVID (2020 onwards)

3. Industry Share and Wages:
   \[ \log(Wage_{ist}) = \beta_0 + \beta_1 Share_{ist} + \alpha_s + \gamma_i + \delta_t + \epsilon_{ist} \]
   - Tests if industries with larger employment shares pay higher wages

4. Wage Premium Persistence:
   \[ Premium_{ist} = \beta_0 + \beta_1 Premium_{is,t-1} + \alpha_s + \gamma_i + \epsilon_{ist} \]
   - Examines if industries that paid above-average wages continue to do so

5. Industry Size and Growth:
   \[ \Delta Employment_{ist} = \beta_0 + \beta_1 \Delta Employment_{is,t-1} + \beta_2 \log(Size_{ist}) + \alpha_s + \gamma_i + \delta_t + \epsilon_{ist} \]
   - Tests if larger industries have different employment growth patterns

6. Employment Concentration and Inequality:
   \[ \log(WageRatio_{st}) = \beta_0 + \beta_1 \log(Concentration_{st}) + \beta_2 \log(TotalEmp_{st}) + \alpha_s + \delta_t + \epsilon_{st} \]
   - Examines if states with more concentrated employment have higher wage inequality

## Long-term Growth Models
7. Employment Trends:
   \[ \log(Employment_{ist}) = \beta_0 + \beta_1 (Year_t - 2007) + \alpha_s + \gamma_i + \epsilon_{ist} \]
   - Shows long-term employment growth trends since 2007

8. Wage Trends:
   \[ \log(Wage_{ist}) = \beta_0 + \beta_1 (Year_t - 2007) + \alpha_s + \gamma_i + \epsilon_{ist} \]
   - Shows long-term wage growth trends since 2007

## Financial Crisis Models
9. Crisis Employment Impact:
   \[ \log(Employment_{ist}) = \beta_0 + \beta_1 PostCrisis_t + \alpha_s + \gamma_i + \epsilon_{ist} \]
   - Shows employment changes after 2008-09 financial crisis

10. Crisis Wage Impact:
    \[ \log(Wage_{ist}) = \beta_0 + \beta_1 PostCrisis_t + \alpha_s + \gamma_i + \epsilon_{ist} \]
    - Shows wage changes after 2008-09 financial crisis

## Industry Structure Models
11. Industry Concentration Trends:
    \[ Share_{ist} = \beta_0 + \beta_1 (Year_t - 2007) + \alpha_s + \gamma_i + \epsilon_{ist} \]
    - Shows if industries are becoming more or less concentrated

12. Wage Inequality Trends:
    \[ \log(WageRatio_{st}) = \beta_0 + \beta_1 (Year_t - 2007) + \beta_2 \log(TotalEmp_{st}) + \alpha_s + \epsilon_{st} \]
    - Shows if wage inequality within states is changing over time

13. Size-Premium Relationship:
    \[ Premium_{ist} = \beta_0 + \beta_1 \log(Size_{ist}) + \beta_2 (Year_t - 2007) + \beta_3 [\log(Size_{ist}) \times (Year_t - 2007)] + \alpha_s + \gamma_i + \epsilon_{ist} \]
    - Tests if larger industries wage premiums evolve differently

## Productivity Models (Four-State Analysis: CA, NY, MI, TX)
14. Long-term Productivity Trends:
    \[ \log(Productivity_{st}) = \beta_0 + \beta_1 (Year_t - 2007) + \alpha_s + \epsilon_{st} \]
    - Shows long-term productivity growth trends since 2007 for major states
    - Captures state-specific productivity trajectories

15. COVID Impact on Productivity:
    \[ \log(Productivity_{st}) = \beta_0 + \beta_1 COVID_t + \alpha_s + \epsilon_{st} \]
    - Shows productivity changes during COVID period across major states
    - Identifies differential impacts across the four largest state economies

16. Productivity Growth Dynamics:
    \[ \Delta Productivity_{st} = \beta_0 + \beta_1 \Delta Productivity_{s,t-1} + \beta_2 \log(Productivity_{st}) + \alpha_s + \epsilon_{st} \]
    - Tests for persistence in productivity growth in major state economies
    - Examines convergence patterns across states

17. Industry Structure and Productivity:
    \[ \log(Productivity_{st}) = \beta_0 + \beta_1 \log(Concentration_{st}) + \beta_2 \log(Wage_{st}) + \alpha_s + \delta_t + \epsilon_{st} \]
    - Examines if industry concentration affects productivity in major states
    - Controls for wage levels and state-specific factors

18. Wage Bill Determinants (Four-State Analysis):
    \[ \Delta WageBill_{st} = \beta_0 + \beta_1 Productivity_{st} + \beta_2 Employment_{ist} + \beta_3 ValueAdded_{ist} + \beta_4 \Delta Employment_{st} + \alpha_s + \delta_t + \epsilon_{ist} \]
    - Examines determinants of changes in state-level wage bills
    - Tests relationships between productivity, employment levels, employment growth, and value added
    - Includes average employment changes across industries
    - Focuses on the four major state economies

Where:
- \(\alpha_s\) represents state fixed effects
- \(\gamma_i\) represents industry fixed effects
- \(\delta_t\) represents year fixed effects
- \(\epsilon_{ist}\) is the error term
- Subscripts: i = industry, s = state, t = year

# Regression Results

```{r, echo=FALSE}
options("modelsummary_format_numeric_latex" = "plain")
modelsummary(models_covid,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "covid_period" = "COVID Period",
    "industry_share" = "Industry Share"
  ),
  title = "COVID Impact Results",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex")
```

```{r, echo=FALSE}
modelsummary(models_industry,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "lag_premium" = "Lagged Premium",
    "lag_pct_change" = "Lagged % Change",
    "industry_size" = "Industry Size",
    "log(employment_concentration)" = "Log Emp Concentration",
    "log(total_employment)" = "Log Total Employment"
  ),
  title = "Industry Structure Results",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(models_trends1,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "year_trend" = "Year Trend",
    "post_crisis" = "Post-Crisis Period"
  ),
  title = "Long-term Growth Results",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```
\newpage
```{r, echo=FALSE}
modelsummary(models_trends2,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "year_trend" = "Year Trend",
    "industry_size" = "Industry Size",
    "industry_size:year_trend" = "Industry Size × Year Trend",
    "log(total_employment)" = "Log Total Employment"
  ),
  title = "Industry Evolution Results",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(reg_prod_trend,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "year_trend" = "Year Trend"
  ),
  title = "Productivity Trends",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(reg_prod_covid,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "covid_period" = "COVID Period"
  ),
  title = "COVID Productivity Impact",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(reg_prod_growth,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "lag(pct_change)" = "Lagged % Change",
    "log(labor_productivity)" = "Log Labor Productivity"
  ),
  title = "Productivity Growth Determinants",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(reg_prod_composition,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "log(employment_concentration)" = "Log Emp Concentration",
    "log(avg_wage)" = "Log Avg Wage"
  ),
  title = "Industry Composition Effect on Productivity",
  notes = list("Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(reg_wage_bill,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "log_productivity" = "Log Productivity",
    "log_employment" = "Log Employment",
    "log_value_added" = "Log Value Added",
    "avg_emp_change" = "Avg Employment Change"
  ),
  title = "Wage Bill Determinants (Four Major States)",
  notes = list(
    "Analysis covers California, New York, Michigan, and Texas",
    "Dependent variable: % Change in State Wage Bill",
    "Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"
  ),
  output = "latex",
  float = FALSE)
```

```{r, echo=FALSE}
modelsummary(models_productivity,
  stars = TRUE,
  gof_map = c("nobs", "r.squared"),
  fmt = "%.3f",
  estimate = "{estimate}{stars}",
  statistic = "({std.error})",
  coef_map = c(
    "year_trend" = "Year Trend",
    "covid_period" = "COVID Period",
    "lag(pct_change)" = "Lagged % Change",
    "log(labor_productivity)" = "Log Productivity",
    "log(employment_concentration)" = "Log Emp Concentration",
    "log(avg_wage)" = "Log Average Wage",
    "log_productivity" = "Log Productivity",
    "log_employment" = "Log Employment",
    "log_value_added" = "Log Value Added"
  ),
  title = "Productivity Analysis Results (Four Major States)",
  notes = list(
    "Analysis covers California, New York, Michigan, and Texas",
    "Significance levels: * p<0.1, ** p<0.05, *** p<0.01",
    "Standard errors in parentheses"
  ),
  output = "latex",
  float = FALSE)
```
